Bird beak's elaboration and innovation

### 2022-10-25 Analysis/05-Figure_with_phylogeny.Rmd
Update 05-Figure_with_phylogeny.Rmd

## Save as png and pdf
ggsave("../Manuscript/Figures/InnovElabTree_main_text.png", innovelab_plot_final, width=12, height=12)
ggsave("../Manuscript/Figures/InnovElabTree_main_text.pdf", innovelab_plot_final, width=12, height=12)

>>>>

## Save as png and pdf
ggsave("../Manuscript/Figures/InnovElabTree_main_text.png", innovelab_plot, width=12, height=12)
ggsave("../Manuscript/Figures/InnovElabTree_main_text.pdf", innovelab_plot, width=12, height=12)
